---
title: "Getting & Cleaning Data Assignment"
author: "Kazim"
date: "15/08/2021"
output: html_document
---

### Project: Cleaning & Getting Data Assignment.

The purpose of this project is to demonstrate ability to collect, work with, and clean a data set.

Data was collected from dowloaded & extracted from UCI HAR Dataset

### Steps Followed to create tidy data set:

1. Downloading of data from given url with download.file command and unzipping in with unzip command.

2. create a list of file routes with file.path command so that it can be read by read.table command.

3. Merging of data sets using rbind command.

4. Extracting mean and standard deviations measurement using grep command.

5. assigning descriptive names to variables using names & gsub command.

6. creating second independent dataset using plyr library.

7. Please refer run_analysis.R script of further details.

### Details of variables are as follows;

1. Values of Varible Activity consist of data from “Y_train.txt” and “Y_test.txt”.

2. Values of Varible Subject consist of data from “subject_train.txt” and subject_test.txt".

3. Values of Varibles Features consist of data from “X_train.txt” and “X_test.txt”.

4. Names of Varibles Features come from “features.txt”
levels of Varible Activity come from “activity_labels.txt”.

Details of variables are below

```{r}
Data <- read.csv("D:/R Programming/Data.txt", sep="")
str(Data)
```
```{r}
```


```{r}
```


